---
title: "BayesiCALLY Questionnaire Validation Report with Confirmatory Factor Analyses"
author: '-----'
date: "`r Sys.Date()`"
output:  word_document
---

This report summarizes the statistical modeling and analysis results associated with **Confirmatory Factor Analysis** (CFA) for Questionnaire Validation. The purpose of this report is to document both estimates of factor loadings (i.e. item-domain correlation, the relative importance of each question/ item/ variable with respect to its factor/ domain) in tables and all statistical outputs for corresponding data modeling in the CFA.


The remainder of this report is organized as follows. Table 1 summarizes factor loadings (i.e. the item-domain correlation) estimates from both frequentist and Bayesian CFA. Output 1 and 2 list all results from the frequentist and Bayesian analyses.

The **Factor Loadings** statistics table that represents estimates of the relative importance of each question with regard to its respective domain is given below. It summarizes the results of **classic frequentist CFA** and **Bayesian CFA**. The item-domain correlation is usually on a scale of 0 to 1, where 0 indicates low relevance of the question/item/variable with respect to its domain/factor and 1 indicates high relevance. The respective confidence and credible intervals are presented below.


Table 1: Factor loadings estimates and their respective confidence intervals and credible intervals for classic frequentist and modern Bayesian CFA.

```{r, echo=FALSE}
library(knitr)
print(kable(formatted.Tableloadings(), type = "pandoc"))
```
\pagebreak

\newpage
Output 1: Summary for classic frequentist CFA.
```{r, echo=FALSE}
print(CFAModelsum())
```
\pagebreak

\newpage
Output 2: Summary for modern Bayesian CFA.
```{r,echo=FALSE}
print(bCFAModelsum())
```

Acknowledgement

The BayesiCALLY web app is developed by Quebec SPOR-SUPPORT Unit at the Department of Family Medicine at McGill University in Canada. Copyright @ Quebec SPOR-SUPPORT. All rights reserved.